\section{Bibliografía}
\begin{thebibliography}{9}
\bibitem{insideairbnb}
Inside Airbnb.
\href{http://insideairbnb.com/}{http://insideairbnb.com/}

\bibitem{insideairbnb-data}
Inside Airbnb - Obtener los datos.
\href{http://insideairbnb.com/get-the-data/}{http://insideairbnb.com/get-the-data/}

\bibitem{insideairbnb-malaga}
Inside Airbnb - Datos de Málaga.
\href{http://insideairbnb.com/malaga}{http://insideairbnb.com/malaga}

\bibitem{youtube1}
YouTube - Data Career Jumpstart.
\href{https://www.youtube.com/watch?v=CHb-QvGcRjw&t=325s&ab_channel=AverySmith-DataCareerJumpstart}{https://youtu.be/CHb-QvGcRjw}

\bibitem{youtube2}
YouTube - AbsentData.
\href{https://www.youtube.com/watch?v=S2zBHmkRbhY&ab_channel=AbsentData}{https://youtu.be/S2zBHmkRbhY}

\bibitem{kaggle1}
Kaggle - Housing Crisis and Tourism in Madrid.
\href{https://www.kaggle.com/code/rusiano/housing-crisis-and-tourism-in-madrid}{https://www.kaggle.com/code/rusiano/housing-crisis-and-tourism-in-madrid}

\bibitem{kaggle2}
Kaggle - Madrid Data Analysis \& Price Prediction.
\href{https://www.kaggle.com/code/viktoriaw/madrid-data-analysis-price-prediction}{https://www.kaggle.com/code/viktoriaw/madrid-data-analysis-price-prediction}

\bibitem{kaggle3}
Kaggle - Data Visualization with Bokeh.
\href{https://www.kaggle.com/code/cindyteh/data-visualization-with-bokeh}{https://www.kaggle.com/code/cindyteh/data-visualization-with-bokeh}

\bibitem{youtube3}
YouTube - Vaibhav Gupta.
\href{https://www.youtube.com/watch?v=9Iq4cM_bAGM&ab_channel=VaibhavGupta}{https://youtu.be/9Iq4cM\_bAGM}

\bibitem{youtube4}
YouTube - Shashank Kalanithi.
\href{https://www.youtube.com/watch?v=pKvWD0f18Pc&ab_channel=ShashankKalanithi}{https://youtu.be/pKvWD0f18Pc}

\bibitem{youtube5}
YouTube - Gaurav Sahani.
\href{https://www.youtube.com/watch?v=bg1Gzo_YvAU&ab_channel=GauravSahani}{https://youtu.be/bg1Gzo\_YvAU}

\bibitem{youtube6}
YouTube - Data Science RoadMap.
\href{https://www.youtube.com/watch?v=47_JlqPxKjY&ab_channel=DataScienceRoadMap}{https://youtu.be/47\_JlqPxKjY}

\bibitem{youtube7}
YouTube - Python Soldiers.
\href{https://www.youtube.com/watch?v=Q2AFVafpRJA&t=776s&ab_channel=PythonSoldiers}{https://youtu.be/Q2AFVafpRJA}

\bibitem{youtube8}
YouTube - Data Science RoadMap.
\href{https://www.youtube.com/watch?v=BTArwS4ljC4&t=61s&ab_channel=DataScienceRoadMap}{https://youtu.be/BTArwS4ljC4}

\bibitem{youtube9}
YouTube - Ashi Ranka.
\href{https://www.youtube.com/watch?v=OFWHY0GJTIM&ab_channel=AshiRanka}{https://youtu.be/OFWHY0GJTIM}

\end{thebibliography}